---
title: "HW3"
author: "Niko&Sid&Sib"
date: "December 27, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Exercise I

```r
set.seed(123)
```
## Question 1

$Joint = f(x_1, x_2, y_1, y_2, \mu_1, \mu_2, \sigma^2) = f(\mu_1)f(\mu_2)f(\sigma^2)f(X_1|\mu_1, \sigma^2)
f(Y_2|\mu_2, \sigma^2)f(X_2|X_1, \mu_2, \sigma^2)f(Y_1|Y_2, \mu_1, \sigma^2)$

## Question 2

Distributions:
$\mu_1$ ~ $N(0,1)$

$\mu_2$ ~ $N(0,1)$

$\sigma^2$ ~ $Exp(3)$

$X_1$ ~ $N(\mu_1,\sigma^2)$

$X_2$ ~ $N(\mu_1,\sigma^2)$

$Y_1$ ~ $N(\mu_1,\sigma^2)$

$Y_2$ ~ $N(\mu_1,\sigma^2)$

Getting $\mu_1$, $\mu_2$,$\sigma$, $x_1$,$x_2$,$y_1$,$y_2$

```{r}
mu1 <- rnorm(1, 0, 1) 
mu2 <- rnorm(1, 0, 1)  
sig <- rexp(1, 3)      
x1 <- rnorm(10000, mu1, sig)   
y2 <- rnorm(10000, mu2, sig)   
y1 <- rnorm(10000, mu1, sig)   
x2 <- rnorm(10000, mu2, sig)   
```

Getting $X_2|X_1$

```{r}
xmu2_1 <- mu2 + cov(x2,x1)*(mean(x1)- mu1)/sig  
xsig2_1 <- sig - cov(x2,x1)*cov(x1,x2)/sig  
x2_1 <- rnorm(10000, xmu2_1, xsig2_1)
```

Getting $Y_1|X_2$
```{r}
ymu1_2 <- mu1 + cov(y1,y2)*(mean(y2)-mu2)/sig   
ysig1_2 <- sig - cov(y1,y2)*cov(y2,y1)/sig  
y1_2 <- rnorm(10000, ymu1_2, ysig1_2)
```

Finally: The Joint Distribution

```{r}
joint = mu1*mu2*sig*x1*y2*x2_1*y1_2
```

## Question 3
```{r, fig.width=5, fig.height=5}
hist(x1,col = 'orchid', main= 'X1', probability = T)
lines(density(x1, adjust=2), col = 'blue', lwd = 4)
```

```{r, fig.width=5, fig.height=5}
hist(y2,col = 'orchid', main= "Y2", probability = T)
lines(density(y2, adjust=2), col = 'blue', lwd = 4)
```

```{r, fig.width=5, fig.height=5}
hist(x2_1,col = 'orchid', main= "X2|1", probability = T)
lines(density(x2_1, adjust=2), col = 'blue', lwd = 4)
```

```{r, fig.width=5, fig.height=5}
hist(y1_2,col = 'orchid', main= "Y1|2", probability = T)
lines(density(y1_2, adjust=2), col = 'blue', lwd = 4)
```

```{r, fig.width=5, fig.height=5}
hist(joint,col = 'orchid', main= "Joint Distribution", probability = T)
lines(density(joint, adjust=2), col = 'blue', lwd = 4)
```

Visually all of the distributions above look Normal.


#Exercise II
## Question 1
### Gaussian Distribution Comparison
```{r}
N_seq = c(10,50,100,500,1000)
Bias_Matrix = matrix(NA, nrow = length(N_seq), ncol = 2)
colnames(Bias_Matrix) = c("Sample Mean", "Median of Mean")
Variance_Matrix = matrix(NA, nrow = length(N_seq), ncol = 2)
colnames(Variance_Matrix) = c("Sample Mean", "Median of Mean")

MSE_Matrix = matrix(NA, nrow = length(N_seq), ncol = 2)
colnames(MSE_Matrix) = c("Sample Mean", "Median of Mean")
Tail_Matrix = matrix(NA, nrow = length(N_seq), ncol = 2)
colnames(Tail_Matrix) = c("Sample Mean", "Median of Mean")


median_of_means=function (x, optimal_block_size)
{
  mean_matrix = matrix(NA,nrow = length(x)/optimal_block_size, ncol=1)
  for (j in 1:length(x)/optimal_block_size)
  {
    mean_matrix[j]=mean(x[optimal_block_size*j])
  }
  out <- median(mean_matrix)
  
}

for (i in 1:length(N_seq))
{
  optimal_block_size= 2
  B = 1000
  est1 = matrix(NA,nrow = B ,ncol = 1)
  est2 = matrix(NA,nrow = B ,ncol = 1)
  for (b in 1:B)
  {
    actual_mean = 3.2
    x = rnorm(N_seq[i],actual_mean,1)
    est1[b,1] = sum(x)/length(x) #estimator1 (Sample Mean)
    est2[b,1] = median_of_means(x,optimal_block_size)  #estimator2 (Median of Samples)
  }
  
  Bias_Matrix[i,1] = mean(est1)-3.2  #E(estimated_theta)-actual_theta
  Bias_Matrix[i,2] = mean(est2)-3.2  #E(estimated_theta)-actual_theta
  
  Variance_Matrix[i,1] = mean((est1)^2)-(mean(est1)^2) #E[x2]-(E[x])2
  Variance_Matrix[i,2] = mean((est2)^2)-(mean(est2)^2) #E[x2]-(E[x])2
  
  MSE_Matrix[i,1] = (Variance_Matrix[i,1])+((Bias_Matrix[i,1])^2) #MSE=var+(bias)2
  MSE_Matrix[i,2] = (Variance_Matrix[i,2])+((Bias_Matrix[i,2])^2) #MSE=var+(bias)2
  
  # Assuming t=2
  t=2
  Tail_Matrix[i,1] <- (var(est1))/(t^2)
  Tail_Matrix[i,2] <- (var(est2))/(t^2)
}
```

Bias Comparison
```{r}
Bias_Matrix
```
Variance Comparison
```{r}
Variance_Matrix
```
MSE Comparison
```{r}
MSE_Matrix
```
Tail Probability Comparison
```{r}
Tail_Matrix
```

### Student Distribution Comparison
```{r}
N_seq = c(10,50,100,500,1000)
Bias_Matrix = matrix(NA, nrow = length(N_seq), ncol = 2)
colnames(Bias_Matrix) = c("Sample Mean", "Median of Mean")
Variance_Matrix = matrix(NA, nrow = length(N_seq), ncol = 2)
colnames(Variance_Matrix) = c("Sample Mean", "Median of Mean")

MSE_Matrix = matrix(NA, nrow = length(N_seq), ncol = 2)
colnames(MSE_Matrix) = c("Sample Mean", "Median of Mean")
Tail_Matrix = matrix(NA, nrow = length(N_seq), ncol = 2)
colnames(Tail_Matrix) = c("Sample Mean", "Median of Mean")


median_of_means=function (x, optimal_block_size)
{
  mean_matrix = matrix(NA,nrow = length(x)/optimal_block_size, ncol=1)
  for (j in 1:length(x)/optimal_block_size)
  {
    mean_matrix[j]=mean(x[optimal_block_size*j])
  }
  out <- median(mean_matrix)
  
}

for (i in 1:length(N_seq))
{
  optimal_block_size= 2
  B = 1000
  est1 = matrix(NA,nrow = B ,ncol = 1)
  est2 = matrix(NA,nrow = B ,ncol = 1)
  for (b in 1:B)
  {
    actual_mean = 0 #Since DF>3 in t-dist, mean equals to 0
    x = rt(N_seq[i],3)
    est1[b,1] = sum(x)/length(x) #estimator1 (Sample Mean)
    est2[b,1] = median_of_means(x,optimal_block_size)  #estimator2 (Median of Samples)
  }
  
  Bias_Matrix[i,1] = mean(est1)-3.2  #E(estimated_theta)-actual_theta
  Bias_Matrix[i,2] = mean(est2)-3.2  #E(estimated_theta)-actual_theta
  
  Variance_Matrix[i,1] = mean((est1)^2)-(mean(est1)^2) #E[x2]-(E[x])2
  Variance_Matrix[i,2] = mean((est2)^2)-(mean(est2)^2) #E[x2]-(E[x])2
  
  MSE_Matrix[i,1] = (Variance_Matrix[i,1])+((Bias_Matrix[i,1])^2) #MSE=var+(bias)2
  MSE_Matrix[i,2] = (Variance_Matrix[i,2])+((Bias_Matrix[i,2])^2) #MSE=var+(bias)2
  
  # Assuming t=2
  t=2
  Tail_Matrix[i,1] <- (var(est1))/(t^2)
  Tail_Matrix[i,2] <- (var(est2))/(t^2)
}
```

Bias Comparison
```{r}
Bias_Matrix
```
Variance Comparison
```{r}
Variance_Matrix
```
MSE Comparison
```{r}
MSE_Matrix
```
Tail Probability Comparison
```{r}
Tail_Matrix
```

### Binomial Distribution Comparison
```{r}
N_seq = c(10,50,100,500,1000)
Bias_Matrix = matrix(NA, nrow = length(N_seq), ncol = 2)
colnames(Bias_Matrix) = c("Sample Mean", "Median of Mean")
Variance_Matrix = matrix(NA, nrow = length(N_seq), ncol = 2)
colnames(Variance_Matrix) = c("Sample Mean", "Median of Mean")

MSE_Matrix = matrix(NA, nrow = length(N_seq), ncol = 2)
colnames(MSE_Matrix) = c("Sample Mean", "Median of Mean")
Tail_Matrix = matrix(NA, nrow = length(N_seq), ncol = 2)
colnames(Tail_Matrix) = c("Sample Mean", "Median of Mean")


median_of_means=function (x, optimal_block_size)
{
  mean_matrix = matrix(NA,nrow = length(x)/optimal_block_size, ncol=1)
  for (j in 1:length(x)/optimal_block_size)
  {
    mean_matrix[j]=mean(x[optimal_block_size*j])
  }
  out <- median(mean_matrix)
  
}

for (i in 1:length(N_seq))
{
  optimal_block_size= 2
  B = 1000
  est1 = matrix(NA,nrow = B ,ncol = 1)
  est2 = matrix(NA,nrow = B ,ncol = 1)
  for (b in 1:B)
  {
    actual_mean = 10000 * 0.35
    x = rbinom(N_seq[i],10000,0.35)
    est1[b,1] = sum(x)/length(x) #estimator1 (Sample Mean)
    est2[b,1] = median_of_means(x,optimal_block_size)  #estimator2 (Median of Samples)
  }
  
  Bias_Matrix[i,1] = mean(est1)-3.2  #E(estimated_theta)-actual_theta
  Bias_Matrix[i,2] = mean(est2)-3.2  #E(estimated_theta)-actual_theta
  
  Variance_Matrix[i,1] = mean((est1)^2)-(mean(est1)^2) #E[x2]-(E[x])2
  Variance_Matrix[i,2] = mean((est2)^2)-(mean(est2)^2) #E[x2]-(E[x])2
  
  MSE_Matrix[i,1] = (Variance_Matrix[i,1])+((Bias_Matrix[i,1])^2) #MSE=var+(bias)2
  MSE_Matrix[i,2] = (Variance_Matrix[i,2])+((Bias_Matrix[i,2])^2) #MSE=var+(bias)2
  
  # Assuming t=2
  t=2
  Tail_Matrix[i,1] <- (var(est1))/(t^2)
  Tail_Matrix[i,2] <- (var(est2))/(t^2)
}
```

Bias Comparison
```{r}
Bias_Matrix
```
Variance Comparison
```{r}
Variance_Matrix
```
MSE Comparison
```{r}
MSE_Matrix
```
Tail Probability Comparison
```{r}
Tail_Matrix
```

## Question 2

### Preparations
```{r}
# Load the data
load("sp500.RData")
# Now some diagnostic plot
par(mfrow = c(1,2))
hist(sp.ind, prob = T, col = "pink", border = "white", breaks = 50,
     xlab = "S&P500 Index", main = "S&P500 log-returns")
lines(density(sp.ind), col = "orchid", lwd = 2)
# Compare the empirical quantiles with the normal quantiles at the
# same level: we see heavy tails and a bit of skewness
qqnorm(sp.ind, pch = 19, cex = .5)
qqline(sp.ind, col = "red")
```

### Non-Parametric Bootstrap

```{r}
# Nonparametric Boostrap
data = sp.ind[1:2700] #Getting the Data, Ommitting the last 80 rows (Just to Make Block Size Simple)
n = length(data) #sample size
B = 1000
N_seq = c(5,10,20,50,100) #Block Sizes
MSE_Boot = matrix(NA, nrow = length(N_seq), ncol = 1)
colnames(MSE_Boot) = c("MSE")
for (i in 1:length(N_seq))
{
  a.nboot = rep (NA,B)
  true_mean = mean(data)
  for (b in 1:B)
  {
    idx <- sample(1:n, replace = T)
    x.boot <- data[idx] #Empirical CDF
    a.nboot = median_of_means(x.boot,N_seq[i])
  } 
  bias = mean(a.nboot)-true_mean
  var = mean((a.nboot)^2) - (mean(a.nboot)^2)
  MSE_Boot [i] = var+(bias)^2
}
```

### Output

MSE
```{r}
print (MSE_Boot)
```

The Best N
```{r}
print (N_seq[which.min(MSE_Boot)])  
```



#Exercise III

### Preparations

```{r}
# Getting Data ------------------------------------------------------------
require(zoo, quietly = T)
require(fImport, quietly = T)
require(tseries, quietly = T)
require(igraph, quietly = T)

# Energy Sector Data Collection
E1 <- coredata(get.hist.quote(instrument="PTR", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))

E2 <- coredata(get.hist.quote(instrument="XOM", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))

E3 <- coredata(get.hist.quote(instrument="CVX", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
E4 <- coredata(get.hist.quote(instrument="TOT", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
E5 <- coredata(get.hist.quote(instrument="SNP", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
# Manufacturing Sector Data Collection
M1 <- coredata(get.hist.quote(instrument="TM", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(M1)

M2 <- (get.hist.quote(instrument="HMC", start="2003-01-01", end="2008-01-01",
                      quote= c("Close"), provider="yahoo", drop=TRUE))
length(M2)

M3 <- coredata(get.hist.quote(instrument="F", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(M3)
M4 <- coredata(get.hist.quote(instrument="GPC", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(M4)
M5 <- coredata(get.hist.quote(instrument="JCI", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(M5)

# Financial Sector Data Collection
F1 <- coredata(get.hist.quote(instrument="WFC", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(F1)

F2 <- coredata(get.hist.quote(instrument="JPM", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(F2)

F3 <- coredata(get.hist.quote(instrument="HSBC", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(F3)
F4 <- coredata(get.hist.quote(instrument="BAC", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(F4)
F5 <- coredata(get.hist.quote(instrument="C", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(F5)

# Healthcare Sector Data Collection
H1 <- coredata(get.hist.quote(instrument="JNJ", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(H1)

H2 <- coredata(get.hist.quote(instrument="PFE", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(H2)

H3 <- coredata(get.hist.quote(instrument="NVS", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(H3)
H4 <- coredata(get.hist.quote(instrument="MRK", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(H4)
H5 <- coredata(get.hist.quote(instrument="UNH", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(H5)

# Services Sector Data Collection
S1 <- coredata(get.hist.quote(instrument="LMT", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(S1)

S2 <- coredata(get.hist.quote(instrument="ACN", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(S2)

S3 <- coredata(get.hist.quote(instrument="CNI", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(S3)
S4 <- coredata(get.hist.quote(instrument="FDX", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(S4)
S5 <- coredata(get.hist.quote(instrument="NOC", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(S5)

# Telecom  Sector Data Collection
T1 <- coredata(get.hist.quote(instrument="T", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(T1)

T2 <- coredata(get.hist.quote(instrument="VZ", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(T2)

T3 <- coredata(get.hist.quote(instrument="CHL", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(T3)
T4 <- coredata(get.hist.quote(instrument="NTT", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(T4)
T5 <- coredata(get.hist.quote(instrument="VOD", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(T5)

# Retail Sector Data Collection
R1 <- coredata(get.hist.quote(instrument="WMT", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(R1)

R2 <- coredata(get.hist.quote(instrument="AMZN", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(R2)

R3 <- coredata(get.hist.quote(instrument="HD", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(R3)
R4 <- coredata(get.hist.quote(instrument="MCD", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(R4)
R5 <- coredata(get.hist.quote(instrument="WBA", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(R5)

# Diversified Business Sector Data Collection
D1 <- coredata(get.hist.quote(instrument="BRK-A", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(D1)

D2 <- coredata(get.hist.quote(instrument="BRK-B", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(D2)

D3 <- coredata(get.hist.quote(instrument="GE", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(D3)
D4 <- coredata(get.hist.quote(instrument="UTX", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(D4)
D5 <- coredata(get.hist.quote(instrument="ABB", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(D5)

# Media Sector Data Collection
Me1 <- coredata(get.hist.quote(instrument="PG", start="2003-01-01", end="2008-01-01",
                               quote= c("Close"), provider="yahoo", drop=TRUE))
length(Me1)

Me2 <- coredata(get.hist.quote(instrument="KO", start="2003-01-01", end="2008-01-01",
                               quote= c("Close"), provider="yahoo", drop=TRUE))
length(Me2)

Me3 <- coredata(get.hist.quote(instrument="CMCSA", start="2003-01-01", end="2008-01-01",
                               quote= c("Close"), provider="yahoo", drop=TRUE))
length(Me3)
Me4 <- coredata(get.hist.quote(instrument="DIS", start="2003-01-01", end="2008-01-01",
                               quote= c("Close"), provider="yahoo", drop=TRUE))
length(Me4)
Me5 <- coredata(get.hist.quote(instrument="UL", start="2003-01-01", end="2008-01-01",
                               quote= c("Close"), provider="yahoo", drop=TRUE))
length(Me5)

# Industrial Data Collection
I1 <- coredata(get.hist.quote(instrument="GE", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(I1)

I2 <- coredata(get.hist.quote(instrument="HON", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(I2)

I3 <- coredata(get.hist.quote(instrument="GD", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(I3)
I4 <- coredata(get.hist.quote(instrument="MMM", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(I4)
I5 <- coredata(get.hist.quote(instrument="UPS", start="2003-01-01", end="2008-01-01",
                              quote= c("Close"), provider="yahoo", drop=TRUE))
length(I5)



```

## Marginal Correlation Graph method

### Correlation matrix, Transformed matrix, Significance matrix
```{r}

#Data Matrix
nodematrix <- matrix(c(E1,E2,E3,E4,E5,M1,M2,M3,M4,M5,F1,F2,F3,F4,F5,H1,H2,H3,H4,H5,S1,S2,S3,
                       S4,S5,T1,T2,T3,T4,T5,R1,R2,R3,R4,R5,D1,D2,D3,D4,D5,Me1,Me2,Me3,Me4,Me5,I1,I2,I3,I4,I5),nrow=length(E1))


x=cor(nodematrix) #correlation matrix



# Z Matrix and Significance Matrix ----------------------------------------
Z = log10((1+x)/(1-x))/2  # H function
m=choose(nrow(x),2)
alpha=0.05
thres=qnorm(1-(alpha/(2*m)))/sqrt(nrow(nodematrix)-1)

Zcap=abs(Z)>thres #signficance matrix

```

### NonParamteric Bootstrap

```{r}
# Bootstrap ---------------------------------------------------------------


B <- 1000
n <- nrow(nodematrix)
a.nboot <- list(rep(NA, B))
for (b in 1:B)
{
  idx <- sample(1:n, replace = TRUE)
  x.boot <- nodematrix[idx,]  # ECDF
  cor.mat <- matrix(NA, nrow=nrow(Z), ncol = ncol(Z))
  for (i in 1:ncol(x)){
    for (j in 1:ncol(x)){
      cor.mat[i,j] <- cor(x.boot[,i], x.boot[,j])
    }
  }
  a.nboot[[b]] <- cor.mat   #Rcap* Bootstrapped samples of correlation matrix 
}


#Delta samples
max_matrix=rep(NA,1000)
for (i in 1:1000)
{
  max_matrix[i]=sqrt(nrow(nodematrix))*max(a.nboot[[i]]-x)   
  
}

ecdf(max_matrix)

#CI for bootstrap
t_alpha = quantile(ecdf(max_matrix),0.05)
lower_bound =  x- (t_alpha)/(sqrt(nrow(nodematrix)))
upper_bound =  x+ (t_alpha)/(sqrt(nrow(nodematrix)))


```

### Plotting graph
```{r}
#plotting graph
i=which(Zcap==TRUE,arr.ind=TRUE)
df <-data.frame(a=i[,1],b=i[,2])
df.g <- simplify(graph.data.frame(d = df[df$a!=df$b, ], directed = FALSE))
k_1=layout_on_grid(df.g, dim = 2)

#color nodes
for (i in 1:50){
  x=V(df.g)$name==i
  if((i-1)%%5==0){
    k=i}
  V(df.g)$color[which(x==TRUE)] <- colors()[k+1]
}

plot(df.g,layout=k_1)


names = c("Energy Sector","Manufacturing Sector","Financial Sector","Healthcare Sector","Services Sector",
          "Telecom Sector","Retail Sector","Diversified Business Sector","Media Sector","Industrial Sector")

legend('topleft',names, 
       lty=1, col=c(colors()[1], colors()[6],colors()[11],colors()[16],colors()[21],colors()[26],colors()[31],colors()[36],colors()[41],colors()[46]), bty='n', cex=.75)



```

## Conclusion 

### Comparison of connections between sectors

```{r}
# 1. Energy sector
# Intracluster connections
nrow(df[df$a < 6 & df$b < 6, ])
# Intercluster connections
nrow(df[df$a < 6 & df$b > 6, ])


# 2. Manufacturing sector
# Intracluster connections
nrow(df[(df$a > 5 & df$a < 11) & (df$b > 5 & df$b < 11), ])
#Intercluster clustering
nrow(df[(df$a > 5 & df$a < 11) & (df$b < 6), ])+ nrow(df[(df$a > 5 & df$a < 11) & (df$b > 11), ])

# 3. Financial sector
# Intracluster connections
nrow(df[(df$a > 10 & df$a < 16) & (df$b > 10 & df$b < 16), ])
#Intercluster clustering
nrow(df[(df$a > 10 & df$a < 16) & (df$b < 11), ])+ nrow(df[(df$a > 10 & df$a < 16) & (df$b > 15), ])

# 4. Healthcare sector
# Intracluster connections
nrow(df[(df$a > 15 & df$a < 21) & (df$b > 15 & df$b < 21), ])
#Intercluster clustering
nrow(df[(df$a > 15 & df$a < 21) & (df$b < 16), ])+ nrow(df[(df$a > 15 & df$a < 21) & (df$b > 20), ])


# 5. Services sector
# Intracluster connections
nrow(df[(df$a > 20 & df$a < 26) & (df$b > 20 & df$b < 26), ])
#Intercluster clustering
nrow(df[(df$a > 20 & df$a < 26) & (df$b < 21), ])+ nrow(df[(df$a > 20 & df$a < 26) & (df$b > 25), ])


# 6. Telecom sector
# Intracluster connections
nrow(df[(df$a > 25 & df$a < 31) & (df$b > 25 & df$b < 31), ])
#Intercluster clustering
nrow(df[(df$a > 25 & df$a < 31) & (df$b < 26), ])+ nrow(df[(df$a > 25 & df$a < 31) & (df$b > 30), ])


# 7. Retail sector
# Intracluster connections
nrow(df[(df$a > 30 & df$a < 36) & (df$b > 30 & df$b < 36), ])
#Intercluster clustering
nrow(df[(df$a > 30 & df$a < 36) & (df$b < 31), ])+ nrow(df[(df$a > 30 & df$a < 36) & (df$b > 35), ])

# 8. Diversified sector
# Intracluster connections
nrow(df[(df$a > 35 & df$a < 41) & (df$b > 35 & df$b < 41), ])
#Intercluster clustering
nrow(df[(df$a > 35 & df$a < 41) & (df$b < 36), ])+ nrow(df[(df$a > 35 & df$a < 41) & (df$b > 40), ])

# 9. Media sector
# Intracluster connections
nrow(df[(df$a > 40 & df$a < 46) & (df$b > 40 & df$b < 46), ])
#Intercluster clustering
nrow(df[(df$a > 40 & df$a < 46) & (df$b < 41), ])+ nrow(df[(df$a > 40 & df$a < 46) & (df$b > 45), ])


# 10. Industrial sector
# Intracluster connections
nrow(df[(df$a > 45 & df$a < 51) & (df$b > 45 & df$b < 51), ])
#Intercluster clustering
nrow(df[(df$a > 45 & df$a < 51) & (df$b < 46), ])+ nrow(df[(df$a > 45 & df$a < 51) & (df$b > 50), ])


```
### Conclusion: From the above outputs it can be observed that intercluster connections are more than intracluster connections i.e. companies of different sectors interact more with each other than the companies interacting within their sectors.  

